The \dealii{} Library, Version 8.5

### 2017-03-10 8.5/paper.tex
Add note; fix typos

\item New code gallery programs demonstrating
  \begin{enumerate}
    \item[(i)] quasi-static visco-elastic material behavior,
    \item[(ii)] multiphase Navier-Stokes flow,
    \item[(iii)] the evolution of global-scale topography on planetary bodies,
    \item[(iv)] goal-oriented elastoplasticity.
  \end{enumerate}

@@

It is envisaged that, in the future, similar can be done for the {\petsc}
iterative solvers.

An additional feature of the \texttt{LinearOperator} suite is the defintion
of a \texttt{schur\_complement} operator and its associated condensation
and post-processing \texttt{PackagedOperation}s. An operator representing
the Schur complement of a block system can be declared and, though the
delayed evaluation offered by \texttt{PackagedOperation}s, reused on any
number of vector systems.

>>>>

\item New code gallery programs demonstrating
\marginpar{Isn't the code gallery itself new for 8.5?}
  \begin{enumerate}
    \item[(i)] quasi-static visco-elastic material behavior,
    \item[(ii)] multiphase Navier-Stokes flow,
    \item[(iii)] the evolution of global-scale topography on planetary bodies,
    \item[(iv)] goal-oriented elastoplasticity.
  \end{enumerate}

@@

We envisage that, in the future, similar can be done for the {\petsc}
iterative solvers.

An additional feature of the \texttt{LinearOperator} suite is the defintion
of a \texttt{schur\_complement} operator and its associated condensation
and post-processing \texttt{PackagedOperation}s. An operator representing
the Schur complement of a block system can be declared and, through the
delayed evaluation offered by \texttt{PackagedOperation}s, reused on any
number of vector systems.
